Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-02-28 Doc/Miccai2013/miccai2013.tex
ADD: overview of "Global deformations"  section
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@529 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In the simulations we used material properties for a porcine liver as
reported by Umale \cite{Umale2013}. The
parenchyma was modeled with elastic modulus 1980~Pa and the capsule has
elastic modulus 8~MPa and thickness 20~$\mu$m.
\TG{values for blood vessels}

@@

Test 1) Global deformation of liver under gravity
  * show that there is a difference between simple homogeneous material
    and material with capsule
  * include blood vessels

>>>>

In the simulations we used material properties for a porcine liver as
reported by Umale \cite{Umale2013}. The
parenchyma was modeled with elastic modulus 1980~Pa and the capsule has
elastic modulus 8~MPa and thickness 20~$\mu$m.
\IP{OK, now we must decide what value we are going to use for the parenchyma, so it does not explode but it's somehow reasonable...)}

\TG{values for blood vessels}

\IP{we have to also add some information how we got the models -- either we comment briefly in each subsection:
Local deformations: cube meshed in gmsh (graded mesh?), number of elements, etc...
Global deformations: contrast-enhanced CT data obtained via acquisition performed on a female pig; the 3D mesh created by a
semi-automatic segmentation using ITKSnap~\cite{itksnap}, then meshed using CGAL~\cite{cgal-meshingAlg} resulting in a mesh having 
NNN elements. The capsule modelled using the surface triangular elements extracted from the tetrahedra. The vascularization 
created from the segmentation of hepatic vein as described in~\cite{peterlik2012}. The structured composed of MMM elements.}

@@

%Test 1) Global deformation of liver under gravity
%  * show that there is a difference between simple homogeneous material
%    and material with capsule
%  * include blood vessels

\IP{Short overview, I'll put it together tomorrow morning and add some fancy images. I am not sure if we are going to mess up 
with gravity, it seems to me too much... We should rather focus only on this "registration-like" simulation (what about 
using term "elastic warping"??? and explain properly why we think it proves the capsule plays a role. My first shot:}

--we want to mimic a process takes place inside the pig such that it results in a natural deformation of the liver

--such a natural deformation happens when the position of the pig is changed from the flank to a supine position

--we performed a segmentation of both flank and supine and for some parts of the liver, displacements up to XXX\,cm  (I would say 3-4) 
were observed, which is enough given the size of the entire liver (18\,cm longest dimension)

--to induce the same deformation on the liver, we performed a process similar to deformation registration between the flank and supine 
data: we chosen a set of feature in flank and supine data such that each feature could be reliably located in both supine and flank 
data

--this set of features was extracted from the vascularization, since although the vascular tree is getting deformed together with the liver, 
the topology remains constant

--then we placed a linear spring to each feature location in the supine data, so it's attracted towards its flank position

--since the features were mapped to the elements via barycentric mapping, the entire model of the liver is being deformed, "elastically warped" from the 
supine to the flank position

--now the tricky part begins: we performed this process with models with and without the capsule; in each case we obtained 
a different resulting shape of liver

--additionally, we measured the forces needed to warp the liver in both cases: we obtained a difference summarized as.... ???
